学術論文

### 2025-05-31 articles.Rmd
update

@@

- [49] Matsumoto, K., Hamatani, S., Kunisato, Y., Mizuno, Y. (2024). Components of cognitive–behavioural therapy for mitigating core symptoms in attention-deficit hyperactivity disorder: a systematic review and network meta-analys. BMJ Ment Health, 27,e301303. https://mentalhealth.bmj.com/content/27/1/e301303

- [48] Ishizu, K.,Ohtsuki, T., Shimoda, Y., Kunisato, Y.(2024). ACT in school settings: A pilot study of ACT-based universal group psycho-educational program among Japanese early adolescents. Journal of Contextual Behavioral Science. DOI: https://doi.org/10.1016/j.jcbs.2024.100851

- [47] Omizu, T. and Kunisato. Y.(2024). Exploring Effective Intervention Strategies for Depression as a Complex System: Targeted Interventions through Network Simulations. Japanese Psychological Research. DOI: https://doi.org/10.1111/jpr.12553 [Code](https://osf.io/ta782/)

- [46] Kashihara, J., Sugawara, D., Kunisato, Y., Takebayashi, Y., Nakajima, S., Ito, M.(2024). Possible Futures for the Psychological Network Approach: Agenda for Clinical Scientists. Japanese Psychological Research. DOI: https://doi.org/10.1111/jpr.12538

>>>>

- [51] Buchanan, E. M.,...Kunisato, Y.,...Suchow, J. (in press). Measuring the Semantic Priming Effect Across Many Languages. Nature Human Behaviour.

### 2025

- [50] Pfuhl, G.,...Kunisato, Y., ...Piotr Sorokowski, P.(2025). A preliminary study on the role of personal history of infectious and parasitic diseases on self-reported health across countries. Public Health, 242, 220–227. [Link](https://doi.org/10.1016/j.puhe.2025.02.030)

- [49] Omizu, T. and Kunisato. Y.(2025). Exploring Effective Intervention Strategies for Depression as a Complex System: Targeted Interventions through Network Simulations. Japanese Psychological Research, 67(2), 147-161. DOI: https://doi.org/10.1111/jpr.12553 [Code](https://osf.io/ta782/)

- [48] Kashihara, J., Sugawara, D., Kunisato, Y., Takebayashi, Y., Nakajima, S., Ito, M.(2025). Possible Futures for the Psychological Network Approach: Agenda for Clinical Scientists. Japanese Psychological Research, 67(2), 132-146. DOI: https://doi.org/10.1111/jpr.12538

@@

- [47] Matsumoto, K., Hamatani, S., Kunisato, Y., Mizuno, Y. (2024). Components of cognitive–behavioural therapy for mitigating core symptoms in attention-deficit hyperactivity disorder: a systematic review and network meta-analys. BMJ Ment Health, 27(1),e301303. https://mentalhealth.bmj.com/content/27/1/e301303

- [46] Ishizu, K.,Ohtsuki, T., Shimoda, Y., Kunisato, Y.(2024). ACT in school settings: A pilot study of ACT-based universal group psycho-educational program among Japanese early adolescents. Journal of Contextual Behavioral Science, 34, 100851. DOI: https://doi.org/10.1016/j.jcbs.2024.100851
